Investigating Neolithic pottery usage in the Yanyuan Basin in Southwest China using organic residue analysis

### 2023-01-13 analysis/paper/paper.Rmd
added details of running parameters to the method section

The GC-MS analysis was performed using an Agilent 7683 B series chromatograph attached to an Agilent 5975 inert mass selective detector. Samples were injected in splitless mode at 320 °C and compounds were separated with a VF-17ms column (60 m length, 0.25 mm i.d., 0.25 μm film thickness). Helium carrier is in constant flow rate of 1.24 ml/min. The temperature of the oven was started from 90 °C for 1 minute, and increased at a rate of 5 °C/min to reach 320 °C , where it was held for 23 min.

>>>>

The GC-MS analysis was performed using an Agilent 7683 B series gas chromatograph attached to an Agilent 5975 inert mass selective detector. Samples were injected in splitless mode at 320 °C and compounds were separated with a VF-17ms column (60 m length, 0.25 mm i.d., 0.25 μm film thickness). Helium carrier is in constant flow rate of 1.3 ml/min. The temperature of the oven was started from 90 °C for 1 minute and increased at a rate of 5 °C/min to 320 °C, where it was held for 23 min. The GC-FID analysis for the FAME samples was carried out using Agilent 6890N gas chromatograph with an FID detector. The GC-C-IRMS analyses of FAMEs of individual fatty acids were conducted using a Thermo Delta V Plus mass spectrometer linked to a GC Trace 1310 through an Isolink Interface. The sample injection volume was 1 ul in toluene and was injected in splitless mode. Separation was carried out using the same model of column for GC-MS and the GC oven temperature was set from 90 °C for 1.5 minutes, and then raised at a rate of 5 °C/min to 320 °C, with an 18-minute hold. Helium was used as a gas carrier in constant flow mode at 1.24 ml/minute.
